Tropopause Evolution in a Rapidly Intensifying Tropical Cyclone: A Static Stability Budget Analysis

### 2017-12-07 paper.tex
Added a couple of equations to Introduction. A few minor revisions to Introduction text.

The static stability can be expressed as the squared Brunt V{\"a}is{\"a}l{\"a} frequency:
   \begin{equation} \label{eq:n2moist}
   EQ. 18 OF BRYAN AND ROTUNNO. ALSO USE EQ. 19
   \end{equation}
In the tropopause layer, $q_s$, $\frac{\partial q_s}{\partial T}$, and $\frac{\partial q_t}{\partial z}$ are small. Assuming that these quantities are zero, Eq. \ref{eq:n2moist} reduces to:
   \begin{equation} \label{eq:n2dry}
   N^2 = \frac{g}{\theta_v}\frac{\partial \theta_v}{\partial z},
   \end{equation}
where \textit{g} is gravitational acceleration and $\theta_v$ is the virtual potential temperature.
To compute $N^2$, CM1 uses Eq. \ref{eq:n2moist} in saturated environments and Eq. \ref{eq:n2dry} in unsaturated environments; for mathematical simplicity, however, only Eq. \ref{eq:n2dry} will be used for the budget computations herein\footnote{The validity of this approximation will be substantiated later in this section.}.

Taking the time derivative of Eq. \ref{eq:n2dry} yields the static stability tendency:

>>>>

The static stability can be expressed as the squared Brunt V{\"a}is{\"a}l{\"a} frequency:
   \begin{equation} \label{eq:n2moist}
   N_m^2 = \frac{g}{T}(\frac{\partial T}{\partial z}+\Gamma_m)(1+\frac{T}{R_d/R_v+q_s}\frac{\partial q_s}{\partial T})-\frac{g}{1+q_t}\frac{\partial q_t}{\partial z},
   \end{equation}
where g is gravitational acceleration, T is temperature, $R_d$ and $R_v$ are the gas constants of dry air and water vapor, respectively, $q_s$ is the saturation mixing ratio, and $q_t$ is the total condensate mixing ratio. $Gamma_m$ is the moist-adiabatic lapse rate:
   \begin{equation} \label{eq:gamma_m}
   \Gamma_m = DETERMINE WHAT THIS IS FOR THE NON-CONSERVATIVE EQUATION SET
   \end {equation}
In the tropopause layer, $q_s$, $\frac{\partial q_s}{\partial T}$, and $\frac{\partial q_t}{\partial z}$ approach zero. In this limiting case, Eq. \ref{eq:n2moist} reduces to:
   \begin{equation} \label{eq:n2dry}
   N^2 = \frac{g}{\theta_v}\frac{\partial \theta_v}{\partial z},
   \end{equation}
where \textit{g} is gravitational acceleration and $\theta_v$ is the virtual potential temperature.
To compute $N^2$, CM1 uses Eq. \ref{eq:n2moist} in saturated environments and Eq. \ref{eq:n2dry} in unsaturated environments; for mathematical simplicity, however, only Eq. \ref{eq:n2dry} will be used for the budget computations herein\footnote{The validity of this approximation will be substantiated later in this section.}.

Taking the time derivative of Eq. \ref{eq:n2dry} yields the static stability tendency:
   \begin{equation} \label{eq:dn2dt}
   \
